---
layout: post
category : lessons
---
{% include JB/setup %}


# Markdown notes
Markdown enables the use of a syntax much more like plain-text email? lets check it!
The output of these syntax can view it at http://bifeng.github.io

1. Headers
# Jekyll-Bootstrap
## Jekyll-Bootstrap
### Jekyll-Bootstrap

2. Links
Use a plain http address or add a link to a phrase:
http://jekyllbootstrap.com
<http://jekyllbootstrap.com>
[semantic versioning](http://semver.org/)

3. Emphasis
Use an asterisk mark to provide emphasis, such as _NOTE_, __NOTE__, *NOTE:*, **NOTE:**.

4. Inline code
To contribute to the framework please make sure to checkout your branch based on `jb-development`!!

5. Horizontal Rule / Page Break
Three or more asterisks or dashes:

********************************
--------------------------------

6. Create lists with a dash:
- Item 1
- Item 2

7. Ordered list:
1. Item 1
2. Item 2
   + Item 2a
   + Item 2b
   
8. Plain Code Blocks
Plain code blocks are displayed in a fixed-width font but not evaulated

```
This text is displayed verbatim / preformatted
```

9. Write 'in-line' code with a black-line and plots:

You can embed an R code chunk like this:
```{r}
summary(cars)
```

You can also embed plots, for example:
```{r, echo=FALSE}
plot(cars)
```

or, more complicated:
```{r qplot, fig.width=4,fig.height=3,message=FALSE}
# quick summary and plot
library(ggplot2)
summary(cars)
qplot(speed,dist,data=cars)+geom_smooth()
```

10. Blockquotes
A friend once said:
> It's always better to give
> than to receive.


R Markdown - Dynamic Documents for R! Exactly what he said!
Reference:<http://rmarkdown.rstudio.com/>













